Case Study (McKenna)

### 2020-09-29 Cases/mrp/Case Study (McKenna) .Rmd
Deleting the second fake case study that was messing with our lives

# This is just some other code that I am working on to try and look at a different way to post. I think this mainly comes from the original case study from Lauren. 
posterior_prob <- posterior_linpred(fit, transform = TRUE, newdata = poststrat)

poststrat_prob <- posterior_prob %*% poststrat$N / sum(poststrat$N)

model_popn_pref <- c(mean = mean(poststrat_prob), sd = sd(poststrat_prob))

round(model_popn_pref, 3)
```

>>>>

# This is just some other code that I am working on to try and look at a different way to post. I think this mainly comes from the original case study from Lauren.

posterior_prob <- posterior_linpred(fit, transform = TRUE, newdata = poststrat)
poststrat_prob <- posterior_prob %*% poststrat$N / sum(poststrat$N)
model_popn_pref <- c(mean = mean(poststrat_prob), sd = sd(poststrat_prob))
round(model_popn_pref, 3)

true_popn_pref <- sum(true_popn$satisfaction * poststrat$N) / sum(poststrat$N)
round(true_popn_pref, 3)

state_df <- data.frame(
  State = 1:50,
  model_state_sd = rep(-1, 50),
  model_state_pref = rep(-1, 50),
  sample_state_pref = rep(-1, 50),
  true_state_pref = rep(-1, 50),
  N = rep(-1, 50)
)

for(i in 1:length(levels(as.factor(poststrat$state)))) {
  poststrat_state <- poststrat[poststrat$state == i, ]
    posterior_prob_state <- posterior_linpred(
    fit,
    transform = TRUE,
    draws = 1000,
    newdata = as.data.frame(poststrat_state)
  )
  poststrat_prob_state <- (posterior_prob_state %*% poststrat_state$N) / sum(poststrat_state$N)
  #This is the estimate for pop in state:
  state_df$model_state_pref[i] <- round(mean(poststrat_prob_state), 4)
  state_df$model_state_sd[i] <- round(sd(poststrat_prob_state), 4)
  #This is the estimate for sample
  state_df$sample_state_pref[i] <- round(mean(sample$cat_pref[sample$state == i]), 4)
  #And what is the actual pop?
  state_df$true_state_pref[i] <-
    round(sum(true_popn$cat_pref[true_popn$state == i] * poststrat_state$N) /
            sum(poststrat_state$N), digits = 4)
  state_df$N[i] <- length(sample$satisfaction[sample$state == i])
}

state_df[c(1,3:6)]
```
